---
title: "STEM Meets Storytelling: Day 1"
output:
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(learnr)
```

## Introduction to R

R is a free open-source programming language commonly used by statisticians and data scientists. "Open-source" means that the software is made and edited by normal people in the world and not specifically by one company. When you create a good community like R has, this means people can create and share amazing things! That's going to be our goal this week.

### 

But before creating amazing things, we need to start small. This is a blank R script:
```{r script_example_1, exercise=TRUE}

```
It's basically like a Google Doc for code. We can type anything we want into the script, and when we hit the "Run Code" button R will submit whatever you type to the computer. Try it out! In the script above, try seeing what happens when you type `2+2` on the line labeled "1" and hit "Run Code".

### 

Did the computer tell you the correct answer?

Scripts also allow us to write multiple lines of code at once, kind of like how you can send a text with multiple sentences in it. What happens when you type `3*3` on line "2" and `4/4` on line "3", and click "Run Code"?
```{r script_example_2, exercise=TRUE}
2+2
```

### 

Hopefully you got 3 different answers! 

### Packages

R comes with some functions pre-loaded, but it would be nice if we could access some functions that other people have made and uploaded. One way to access that code is by installing something called a "package".

A package is just a bunch of functions that someone has written, bundled together, and uploaded to the Comprehensive R Archive Network (or CRAN). Currently, there are about 18,641 packages on CRAN available for installation!

We install a packages by using the function `install.packages()`, and putting the package name inside the parentheses in double-quotes. Installing a package is like buying a book and putting it on your bookshelf.

Once the package is installed, you need to tell R to open it up. We do this using the `library()` function, and putting the package name inside the parentheses *without* using quotation marks. This is like taking a book off your shelf and opening it up to read. Once you do this, you have access to all the functions in the package!

### Data Types

Did you know there are different types of data? 